Preprocessing: filtering

### 2022-09-14 analysis/filtering.Rmd
finished onset corrections
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

>>>>

# Individual investigation
If the performance has complicated pitch errors, investigate individually.

```{r}
# combine error
error_onset <- rbind(error_extra_onset, error_missing_onset, error_sub_onset)

error_ind_onset <- error_onset[startsWith(CorrectionNr, "Check")]
error_ind_onset
```

1) SubNr: 12, TrialNr: 13

```{r, include = FALSE}
current_1 <- dt_onset[SubNr == error_ind_onset$SubNr[1] & TrialNr == error_ind_onset$TrialNr[1]]
current_1$RowNr <- c(1:nrow(current_1))
current_1$Ideal <- c(dt_ideal$Pitch, rep(NA, abs(nrow(current_1) - nrow(dt_ideal))))
graph(current_1)

# remove the first error
current_1 <- edit(current_1, dt_ideal)
current_1$Ideal <- dt_ideal$Pitch
graph(current_1)

# corrected the second error (substituted note)
current_1 <- edit(current_1, dt_ideal)
graph(current_1)

error_ind_onset$CorrectionNr[1] <- 2
```

2) SubNr: 10, TrialNr: 10

```{r, include = FALSE}
current_2 <- dt_onset[SubNr == error_ind_onset$SubNr[2] & TrialNr == error_ind_onset$TrialNr[2]]
current_2 <- insert_na(current_2, dt_ideal)
current_2$RowNr <- c(1:nrow(current_2))
current_2$Ideal <- dt_ideal$Pitch
graph(current_2)

# insert one skipped note
current_2 <- edit(current_2, dt_ideal)
current_2$Ideal <- dt_ideal$Pitch
current_2$RowNr <- 1:nrow(current_2)
graph(current_2)

# remove an extra note
current_2 <- edit(current_2, dt_ideal)
current_2$Ideal <- dt_ideal$Pitch
graph(current_2)

error_ind_onset$CorrectionNr[2] <- 3
```

3) SubNr

```{r, include = FALSE}
current_3 <- dt_onset[SubNr == error_ind_onset$SubNr[3] & TrialNr == error_ind_onset$TrialNr[3]]

```

```{r, include = FALSE}
# combine error
error_offset <- rbind(error_extra_offset, error_missing_offset, error_sub_offset)

error_ind_offset <- error_offset[startsWith(CorrectionNr, "Check")]
error_ind_offset
```
